### 2021-11-09 README.Rmd
binder not working - remove badge

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/bbartholdy/byoc-starch/main?urlpath=rstudio) 
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.5604670.svg)](https://doi.org/10.5281/zenodo.5604670)

>>>>

<!--[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/bbartholdy/byoc-starch/main?urlpath=rstudio)--> 
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.5604670.svg)](https://doi.org/10.5281/zenodo.5604670)
